General constraints on magic distillation protocols from statistical mechanics

### 2021-04-18 appendix.tex
Blending of new perspective. Bits need checking for logical/detail gaps.

In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{n}\id$ with uniform Wigner distribution $\frac{1}{n}\bm{1} = (\frac{1}{n},\dots,\frac{1}{n})$.
This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
\begin{proposition}\label{prop:major}
Given $\bmx, \bmy \in \mathbb{R}^n$ the following statements are equivalent:
 \begin{enumerate}
	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
	\item[(iii)]\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{n}\bm{1}}(t)$.
 \end{enumerate}
\end{proposition}
	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem and is taken as our definition of majorisation in the main text.

@@

\subsection{Embedding map}

>>>>

In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{n}\id$ with uniform Wigner distribution $\frac{1}{n}\bm{1} = (\frac{1}{n},\dots,\frac{1}{n})$.
This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
\begin{proposition}\label{prop:major}
Given $\bmx, \bmy \in \mathbb{R}^n$ the following statements are equivalent:
 \begin{enumerate}
	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
\end{theorem}
	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
	\item[(iii)]\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{n}\bm{1}}(t)$.
 \end{enumerate}
\end{proposition}
	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem and is taken as our definition of majorisation in the main text.

@@

\begin{lemma} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
\end{lemma}\label{lemma:Lorenz_linearity}
\begin{proof} The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order. However since $a > 0$, this is the same permutation that puts  $(p_i/r_i)$ in non-increasing order. We thus have
\begin{equation}
(\sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)}) = (\sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)}) \nonumber,
\end{equation}
therefore the value of the Lorenz function at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
\begin{equation}
L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b x_k,
\end{equation}
and so from linearity, we have in general $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any intermediate $x$.
\end{proof}
\subsection{Embedding map}
